### 2018-01-15 latex/MOSIM2018/article.tex
changes in MOSIM article: renaming of parameters and state of the art

    There is a fixed set of $j \in \mathcal{J}$ tasks to be accomplished over an horizon of time divided into $t \in \mathcal{T}$ discrete periods. In order to be accomplished, these tasks require the assignment of a specific number of resources $r_{j}$ each period of time the task is active. Tasks have both a fixed start and end time that define the set of periods of time it is active.

    During each assigned period, tasks use the assigned resources for a time $h_j$.

    The assignment of a resource to a task is not decided for the whole duration of the task. After a minimum amount of time ($mt$), a resource can be freed and exchanged for another one, even if the task it is assigned to has not finished. The total number of resources being used at any given time in a specific task can never be less than the required $r_{j}$.

@@

    Maintenances have a fix duration of $m$ periods.

@@

@@

  Lastly, in \cite{Chastellux2017} a mission-centered modeled is presented. Here, cycles, composed of one maintenance followed by mission assignments were used. Instances of 6 - 70 aircraft and 60 monthly periods were tested, founding close to optimal solutions for small to medium instances using MIP formulations and heuristics based on these MIP formulations.

@@

    \begin{tabular}{p{8mm}p{67mm}}
        $h_j$             & amount of usage time for resources used in task $j$. \\
        $r_j$             & amount of resources that task $j$ needs when active. \\
        $mt$              & minimum number of periods a resource can be assigned to a task. \\
        % $aut_i$           & maximal absolute usage time for resource $i$. \\
        % $aet_i$           & maximal absolute elapsed time for resource $i$. \\
        $m$               & maintenance duration in number of periods. \\
        $E$               & remaining elapsed time after a maintenance. \\
        $H$               & remaining usage time after a maintenance. \\
        % $S$               & remaining storage time after (certain) maintenances. \\
        $w_1$               & weight of smoothness for maintenances. \\
        $w_2$               & weight of smoothness for unavailabilities. \\
        $n_t$             & number of resources in already-planned maintenance in period $t$.\\
        $d_t$             & number of resources that need to be assigned in total in period $t$. \\
        $rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning period. \\
        $ret^{Init}_{i}$  & remaining elapsed time for resource $i$ at the start of the planning period. \\
        $ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning period. \\
        $rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning period. \\
    \end{tabular}

@@

    \begin{tabular}{p{8mm}p{67mm}}
        $A_{jti}$   &  1 if task $j \in J$ in period $t\in \mathcal{T}_j$ is realized with resource $i \in \mathcal{I}_j$, 0 otherwise. \\  
        $M_{it}$    &  1 if resource $i \in I$ starts maintenance in period $t \in \mathcal{T}$, 0 otherwise. \\
        $rut_{it}$  &  remaining usage time (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        $ret_{it}$  &  remaining elapsed time (integer) for resource $i$ after period $t \in \mathcal{T}0$. \\  
        $U_{max}$   &  maximal number (integer) of unavailable resources in any period. \\
        $M_{max}$   &  maximal number (integer) of resources in maintenance in any period. \\
    \end{tabular}

    Note that  $A_{jti}$ and $M_{it}$ are initially set up to 0 for all resources already in maintenance at the beginning of the planning period for the remaining time periods of maintenance. The remaining usage time for each resource at the beginning of the planning period is used to initialize $rut_{i0}$.

@@

    \begin{align}
        & \text{Min}\; w_1 \times M_{max} + w_2 \times U_{max}
    \end{align}
    where weights $w_1$ and $w_2$ are chosen by the decision maker. 
    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} M_{it'} + n_{t} \leq M_{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
               % maximum capacity2:                
        %        & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} \leq M_{max}
        % & t =m, ..., |\mathcal{T}|  \label{eq:capacity2}\\
               %avail
       & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} M_{it'} + n_{t} \notag \\
           &\hspace*{10mm}+ d_t\leq U_{max} 
        &t \in \mathcal{T} \label{eq:avalaibility1}\\
               % maximum capacity2:                
        %        & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} M_{it'} + d_t\leq U_{max} 
        % & t =m, ..., |\mathcal{T}|  \label{eq:avalaibility2}\\
        & \sum_{i \in \mathcal{I}_j} A_{jti} = r_{j}
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        & \sum_{t' \in \mathcal{T}^{s}_t} M_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} A_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

    Maintenance capacity is controlled by (\ref{eq:capacity1}). The number of unavailable resources is defined by (\ref{eq:avalaibility1}). Tasks' resource requirements are defined by (\ref{eq:taskres}). Constraints (\ref{eq:state}) guarantee that a resource can be used only for one task or maintenance operation at the same period.  
    \begin{align}
        % remaining used time
         & rut_{it} \leq rut_{it-1} + H M_{it} \notag \\ 
           &\hspace*{4mm}- \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} A_{jti} h_{j} \notag \\
                && t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\
        & rut_{i0} = rut^{Init}_i
               & i \in \mathcal{I} \label{eq:rut_initial}\\
        & rut_{it} \geq H M_{it}
                & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rut_lower}\\ 
        & rut_{it} \in [0,H]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu} \\
        & ret_{it} \leq ret_{it-1} - 1 \notag \\
          &\hspace*{4mm}+ E M_{it}
                & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:ret_upper}\\
        & ret_{i0} = ret^{Init}_r
                & i \in \mathcal{I} \label{eq:ret_initial}\\
        & ret_{it} \geq E M_{it}
                & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:ret_lower}\\                 
        & ret_{it} \in [0,me]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:me}\\
        & \sum_{i \in \mathcal{I}} ret_{it} \geq ret^{Init}_{sum}
              & t = |\mathcal{T}| \label{eq:min_ret}\\
        & \sum_{i \in \mathcal{I}} rut_{it} \geq rut^{Init}_{sum}
              & t = |\mathcal{T}| \label{eq:min_rut}
    \end{align}
        % These constraints calculate the balances of hours for each resource.
    The remaining usage time is defined by (\ref{eq:rut_upper})-(\ref{eq:rut_initial}) and its limits by (\ref{eq:rut_lower})-(\ref{eq:mu}). 
    Similarly, the remaining elapsed time is defined by (\ref{eq:ret_upper})-(\ref{eq:ret_initial}) and its limits by (\ref{eq:ret_lower})-(\ref{eq:me}). 
    Finally, \ref{eq:min_ret} and \ref{eq:min_rut} guarantee that resources have, globally, the same number of remaining used and elapsed times that at the beginning.

@@

@@

    In order to understand the sensibility of the weights $w_1$ and $w_2$ on the solution, a bi-objective analysis was done. In it, both weights were changed between 0 and 1 in intervals of 0.1 so that they always summed 1. Table \ref{tab:multiobj} shows the obtained results for each instance. The base instance that was used for this comparison was the one of 21 periods and 9 tasks corresponding to id 1331.

>>>>

    There is a fixed set of $j \in \mathcal{J}$ tasks to be accomplished over an horizon of time divided into $t \in \mathcal{T}$ discrete periods. In order to be accomplished, these tasks require the assignment of a specific number of resources $R_j$ each period of time the task is active. Tasks have both a fixed start and end time that define the set of periods of time it is active.

    During each assigned period, tasks use the assigned resources for a time $H_j$.

    The assignment of a resource to a task is not decided for the whole duration of the task. After a minimum amount of time ($MT$), a resource can be freed and exchanged for another one, even if the task it is assigned to has not finished. The total number of resources being used at any given time in a specific task can never be less than the required $R_j$.

@@

    Maintenances have a fix duration of $M$ periods.

@@

  In \cite{Verhoeff2015}, a model for the Royal Netherlands Air Force was developed. Here, three criteria for improving the planning robustness are presented and applied in a MIP model: availability, serviceability and sustainability.

  With respect to heuristic methods for solving this problem, both \cite{Kozanidis2008} and \cite{Cho2011} already presented alternatives to the MIP formulation for solving bigger instances with reduced scope. In \cite{steiner2006heuristic}, a constructive, stepped heuristic approach is described to obtain balanced maintenances for the Swiss Air Force. Both calendar-based maintenances actions (CBMA) and usage-based maintenance actions (UBMA) are used. In \cite{gavranis2015exact}, an exact algorithm was presented and tested on instances of 6 periods and between 10 and 200 aircraft for the special case of maximizing the residual flight time availability or total remaining usage time. Finally, in \cite{kozanidis2014heuristics}, two heuristics to solve big instances of the problem by taking consecutive decisions period by period with the help of mathematical models at each step.

  Regarding operational-level planning, a more detailed implementation is found in \cite{safaei2011workforce}, where the specific conditions during the maintenances operations are taken into account to schedule the maintenance jobs, such as the workforce skills and availability.

@@

  Lastly, in \cite{Chastellux2016} a mission-centered modeled is presented. Here, cycles, composed of one maintenance followed by mission assignments were used. Instances of 6 - 70 aircraft and 60 monthly periods were tested, founding close to optimal solutions for small to medium instances using MIP formulations and heuristics based on these MIP formulations.

@@

    \begin{tabular}{p{8mm}p{67mm}}
        $H_j$             & amount of usage time for resources used in task $j$. \\
        $R_j$             & amount of resources that task $j$ needs when active. \\
        $MT$              & minimum number of periods a resource can be assigned to a task. \\
        % $aut_i$           & maximal absolute usage time for resource $i$. \\
        % $aet_i$           & maximal absolute elapsed time for resource $i$. \\
        $M$               & maintenance duration in number of periods. \\
        $E$               & remaining elapsed time after a maintenance. \\
        $H$               & remaining usage time after a maintenance. \\
        % $S$               & remaining storage time after (certain) maintenances. \\
        $W_1$               & weight of smoothness for maintenances. \\
        $W_2$               & weight of smoothness for unavailabilities. \\
        $N_t$             & number of resources in already-planned maintenance in period $t$.\\
        $D_t$             & number of resources that need to be assigned in total in period $t$. \\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning period. \\
        $Ret^{Init}_{i}$  & remaining elapsed time for resource $i$ at the start of the planning period. \\
        $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning period. \\
        $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning period. \\
    \end{tabular}

@@

    \begin{tabular}{p{8mm}p{67mm}}
        $a_{jti}$   &  1 if task $j \in J$ in period $t\in \mathcal{T}_j$ is realized with resource $i \in \mathcal{I}_j$, 0 otherwise. \\  
        $m_{it}$    &  1 if resource $i \in I$ starts maintenance in period $t \in \mathcal{T}$, 0 otherwise. \\
        $rut_{it}$  &  remaining usage time (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        $ret_{it}$  &  remaining elapsed time (integer) for resource $i$ after period $t \in \mathcal{T}0$. \\  
        $u_{max}$   &  maximal number (integer) of unavailable resources in any period. \\
        $m_{max}$   &  maximal number (integer) of resources in maintenance in any period. \\
    \end{tabular}

    Note that  $a_{jti}$ and $m_{it}$ are initially set up to 0 for all resources already in maintenance at the beginning of the planning period for the remaining time periods of maintenance. The remaining usage time for each resource at the beginning of the planning period is used to initialize $rut_{i0}$.

@@

    \begin{align}
        & \text{Min}\; W_1 m_{max} + W_2 u_{max}
    \end{align}
    where weights $W_1$ and $W_2$ are chosen by the decision maker. 
    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq m_{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
               % maximum capacity2:                
        %        & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} m_{it'} \leq m_{max}
        % & t =m, ..., |\mathcal{T}|  \label{eq:capacity2}\\
               %avail
       & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \notag \\
           &\hspace*{10mm}+ D_t\leq u_{max} 
        &t \in \mathcal{T} \label{eq:avalaibility1}\\
               % maximum capacity2:                
        %        & \sum_{t' = t - m+1}^{t} \,\, \sum_{i \in \mathcal{I}} m_{it'} + D_t\leq u_{max} 
        % & t =m, ..., |\mathcal{T}|  \label{eq:avalaibility2}\\
        & \sum_{i \in \mathcal{I}_j} a_{jti} = R_j
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        & \sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

    Maintenance capacity is controlled by (\ref{eq:capacity1}). The number of unavailable resources is defined by (\ref{eq:avalaibility1}). Tasks' resource requirements are defined by (\ref{eq:taskres}). Constraints (\ref{eq:state}) guarantee that a resource can be used only for one task or maintenance operation at the same period.  
    \begin{align}
        % remaining used time
         & rut_{it} \leq rut_{it-1} + H m_{it} \notag \\ 
           &\hspace*{4mm}- \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} H_j \notag \\
                && t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:rut_upper}\\
        & rut_{i0} = Rut^{Init}_i
               & i \in \mathcal{I} \label{eq:rut_initial}\\
        & rut_{it} \geq H m_{it}
                & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:rut_lower}\\ 
        & rut_{it} \in [0,H]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:mu} \\
        & ret_{it} \leq ret_{it-1} - 1 \notag \\
          &\hspace*{4mm}+ E m_{it}
                & t =1, ..., \mathcal{T}, i \in \mathcal{I} \label{eq:ret_upper}\\
        & ret_{i0} = Ret^{Init}_i
                & i \in \mathcal{I} \label{eq:ret_initial}\\
        & ret_{it} \geq E m_{it}
                & t \in \mathcal{T}, i \in \mathcal{I}\label{eq:ret_lower}\\                 
        & ret_{it} \in [0,me]
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:me}\\
        & \sum_{i \in \mathcal{I}} ret_{it} \geq Ret^{Init}_{sum}
              & t = |\mathcal{T}| \label{eq:min_ret}\\
        & \sum_{i \in \mathcal{I}} rut_{it} \geq Rut^{Init}_{sum}
              & t = |\mathcal{T}| \label{eq:min_rut}
    \end{align}
        % These constraints calculate the balances of hours for each resource.
    The remaining usage time is defined by (\ref{eq:rut_upper})-(\ref{eq:rut_initial}) and its limits by (\ref{eq:rut_lower})-(\ref{eq:mu}). 
    Similarly, the remaining elapsed time is defined by (\ref{eq:ret_upper})-(\ref{eq:ret_initial}) and its limits by (\ref{eq:ret_lower})-(\ref{eq:me}). 
    Finally, \ref{eq:min_ret} and \ref{eq:min_rut} guarantee that resources have, globally, the same number of remaining used and elapsed times that at the beginning.

@@

  \begin{table}
  \begin{center}

@@

    In order to understand the sensibility of the weights $W_1$ and $W_2$ on the solution, a bi-objective analysis was done. In it, both weights were changed between 0 and 1 in intervals of 0.1 so that they always summed 1. Table \ref{tab:multiobj} shows the obtained results for each instance. The base instance that was used for this comparison was the one of 21 periods and 9 tasks corresponding to id 1331.
